04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
now with all genes?

  tvsd <- tvsd[, sample(ncol(tvsd), 20)] # select 20 random genes
  tvsd$V1 <- row.names(tvsd)             # prep for joining

@@

  # LDA analysis

  # Fit the model
  print(model <- lda(treatment~ sex, data = train.transformed))
  # Make predictions
  print(predictions <- model %>% predict(test.transformed))
# Model accuracy
  print(mean(predictions$class==test.transformed$treatment))

>>>>

  #tvsd <- tvsd[, sample(ncol(tvsd), 20)] # select 20 random genes
  tvsd$V1 <- row.names(tvsd)             # prep for joining

@@

  # LDA analysis
  # Fit the model
  print(model <- lda(treatment~ sex, data = train.transformed))
  # Make predictions
  print(predictions <- model %>% predict(test.transformed))
# Model accuracy
  print(mean(predictions$class==test.transformed$treatment))
